Astr 513: Homework 2

### 2016-03-09 HW2/HW2.tex
Fixed a typo and fixed some of part b.
I noticed a typo in part d, so I went ahead and fixed that. I haven’t
compiled yet because of the empty equation environment towards the end,
but I didn’t change any syntax, so it should still work.

 \item Now we use Monte Carlo realizations of $R$, $g$, and $h$ assuming Gaussian uncertainties to find the distributions of $u_x$ and $u_y$. Using this method, we find that $u_x \approx 11.1\substack{+1.32 \\ -0.99}$ and $u_y \approx 4.43\substack{+0.42 \\ -0.46}$. So the means for $u_x$ and $u_y$ seem to agree with the error propagation method, but not the errors. The marginalized distributions for $u_x$ and $u_y$, as well as the distribution of $u_y$ vs $u_x$, can be seen in the corner plot in Fig ~\ref{fig:2.1b}.

@@

\section{Part D}
Bayes' Theorem says
\begin{equation}
  P(A|B) = \frac{P(B|A)P(A)}{P(B)}
\end{equation}
where $P(X|Y)$ is a conditional probability of $X$ given $Y$, and $P(Z)$ is 
refered to as a \textit{prior} belief on what the value of $Z$ should be.
Frequentists equate the two conditional probabilities, but this is incorrect
in the Bayesian approach precisely because you wish to be informed by the 
priors. In this part, we assume \textit{uniform} priors on our posterior
parameters $u_x$, $u_y$ and $g$, and in addition to this there is no Jacobian 
transformation. Thus we can write for the conditional probability
\begin{equation}

>>>>

 \item Now we use Monte Carlo realizations of $R$, $g$, and $h$ assuming Gaussian uncertainties to find the distributions of $u_x$ and $u_y$. Using this method, we find that $u_x \approx 11.1\substack{+1.32 \\ -0.99}$ and $u_y \approx 4.43\substack{+0.42 \\ -0.46}$. So the means and errors for $u_x$ and $u_y$ seem to agree with the error propagation method. The marginalized distributions for $u_x$ and $u_y$, as well as the distribution of $u_y$ vs $u_x$, can be seen in the corner plot in Fig ~\ref{fig:2.1b}.

@@

\section{Part D}
Bayes' Theorem says
\begin{equation}
  P(A|B) = \frac{P(B|A)P(A)}{P(B)}
\end{equation}
where $P(X|Y)$ is a conditional probability of $X$ given $Y$, and $P(Z)$ is 
referred to as a \textit{prior} belief on what the value of $Z$ should be.
Frequentists equate the two conditional probabilities, but this is incorrect
in the Bayesian approach precisely because you wish to be informed by the 
priors. In this part, we assume \textit{uniform} priors on our posterior
parameters $u_x$, $u_y$ and $g$, and in addition to this there is no Jacobian 
transformation. Thus we can write for the conditional probability
\begin{equation}
